You can be Shakespeare! \\ A Case Study in Paraphrase Targeting Writing Styles

### 2012-08-27 paper/paper_wei.tex
fixed the table
Finished the description of dict-based baseline. Note that two tables are also modified.

We gathered a set of 2,386  dictionary entries which were scraped from \url{http:/www.william-shakespeare.info} and semi-automaticaly cleaned.  Example
dictionary entries are presented in table \ref{dictionary_example}.

{\bf TODO:} need to describe how parameters were learned and combined with LM

\begin{table}
  \begin{center}
  \begin{tabular}{|l|l||l|l|}
    \hline
    target & source & target & source \\
    \hline
    \hline
    ABATE & shorten & ANIGHT & by night \\
    \hline
    CAUTEL & deceit & CHILDING & pregnant \\
    \hline
    FOIL & defeat & MORTAL & deadly \\
    \hline
  \end{tabular}
  \end{center}
  \caption{Exaple dictionary entries}
  \label{dictionary_example}
\end{table}

\subsubsection{Out of Domain Monolingual Parallel Data}
As a final baseline we consider a paraphrase system which is trained on out-of-domain data gathered by asking users of Amazon's Mechanical Turk Service 
\cite{Snow08} to describe videos \cite{chen11}.  We combine a phrase table extracted from this out of doimain parallel text, with an in-domain
language model consisting of Shakespeare's 37 plays.  Although this monolingual parallel data does not include text in the target writing style,
the in-domain language model does bias the generated sentences towards Shakespeare's writing style.

\subsection{Comparison Using Existing Automatic Evaluation Metrics}
Figure \ref{bleupinc} compares a variety of sytstems targeting Shakesperean English using previously the previosly proposed BLEU \cite{Papineni02} and PINC \cite{chen11} automatic evaluation metrics.  A summary of each system is presented in table \ref{systems}.  Notice that the enotes data is quite similar to the original translations,
obtaining a BLEU score of 52.3 when compared against the original text.  Our goal is to produce paraphrases which make many changes to the input, therefore
in the remainder of this paper, we focus our evaluation on the Sparknotes data for evaluation.

@@

\begin{table}
  \begin{center}
    \begin{tabular}{|l|p{3in}|}
      \hline
      System & Description \\
      \hline
      \hline
      16and7plays\_36LM & Phrase table learned from all 16 Sparknotes plays (other than R\&J) and language model built from all 36 of Shakespeare's plays, excluding R\&J.
      Uses default Moses parameters. \\
      \hline
      16and7plays\_36LM\_MERT & Same as 16and7plays\_36LM except parameters are tuned using Minimum Error Rate Training instead of using the default Moses parameters.\\
      \hline
      16and7plays\_16LM & Phrase table is built from both Sparknotes and Enotes data, and Language model is built from the 16 with modern translations\\
      \hline
      16and7plays\_16LM\_MERT & Same as 16and7plays\_16LM except parameters are tuned using MERT. \\
      \hline
      16plays\_36LM & Only Sparknotes modern translations are used.  All 36 plays are used to train Shakesperean language model. a\\
      \hline
      16plays\_36LM\_MERT & Same as 16plays\_36LM except parameters are tuned using MERT. \\
      \hline
      modern (no change) & No changes are made to the input, modern translations are left unchanged. \\
      \hline
      Dictionary & Dictionary baseline described in section \ref{dictionary_baseline}\\
      \hline
    \end{tabular}
  \end{center}
  \caption{Descriptions of various systems for Shakesperean Paraphrase.  Romeo and Juliet is held out for testing.}
  \label{systems}
\end{table}

\begin{figure}
  \begin{center}
    \begin{tabular}{cc}
      \includegraphics[width=2.4in]{figures/bleupinc1.pdf} & \includegraphics[width=2.4in]{figures/bleupinc2.pdf} \\
    \end{tabular}
  \end{center}
  \caption{Various Shakesperean Paraphrase systems compared using BLEU and PINC.}
  \label{bleupinc}
\end{figure}

@@

\begin{table}
  \begin{center}
    \begin{tabular}{|l|l|p{1.4in}|p{1.4in}|}
      \hline
      Source & Speaker & Input & Output \\
      \hline
      \hline
      Romeo \& Juliet & Benvolio & he killed your relative , brave mercutio , and then young romeo killed him . & he slew thy kinsman , brave mercutio , and then young romeo kill him . \\
      \hline
      Romeo \& Juliet & Romeo & i can read my own fortune in my misery . & i can read mine own fortune in my woes . \\
      \hline
      Star Wars & Palpatine & If you will not be turned, you will be destroyed! & if you will not be turn 'd , you will be undone ! \\
      \hline
      Star Wars & Luke & Father, please! Help me! & father , i pray you , help me ! \\    
      \hline
      The Matrix & Agent Smith & Good bye, Mr. Anderson. & fare you well , good master anderson . \\
      \hline
      The Matrix & Morpheus & I'm trying to free your mind, Neo. But I can only show you the door. You're the one that has to walk through it. & i 'll to free your mind , neo. but i can but show you the door. you 're the one that hath to tread it . \\
      \hline
      Raiders of the Lost Ark & Belloq & Good afternoon, Dr. Jones. & well met , dr. jones . \\
      \hline
      Raiders of the Lost Ark & Jones & I ought to kill you right now. & i should kill thee straight . \\
      \hline
    \end{tabular}
  \end{center}
  \caption{Example Shakesperean paraphrases generated by the best overall system.}
\end{table}

\section{Human Evaluation}
Figure \ref{bleupinc} provides some insight into the performance of the various systems, however it is innitially unclear how well the BLEU and PINC
automatic evaluation metrics perform when applied to evaluating paraphrases targeting a specific style of writing.  BLEU and PINC have previously
been shown to have high correlation with human judgements of semantic adequacy and lexical dissimilarity of paraphrase candidates, however no
previous work has evaluated automatically generated paraphrases which target a specific style of writing \cite{chen11}.

@@

For this purpose, we randomly sampled 100 lines from Romeo and Juliet, then two of the authors annotated each sentence and it's Shakesperean
translation with semantic adequacy, lexical dissimilarity, stylistic similarity, and overal quality.
The aggregate results of the human evaluation are displayed in figure \ref{human_judgements}.

\begin{figure}
  \begin{center}
    \includegraphics[width=4in]{figures/human_judgements.pdf}
  \end{center}
  \caption{Average human judgements evaluating semantic adequacy, lexical dissimilarity, stylistic similarity, and overall quality
    of Shakesperean paraphrase systems} 
  \label{human_judgements}
\end{figure}

%Argue why BLEU might capture writing style in addition to semantic adequacy
%Argue that we really want to seperate these two measures
%Present initial results from human evaluation (plot? - table?)
%Plot style vs. equivelance...?

\section{New Metrics Evaluating Writing Style}

\section{Experiments}
\begin{itemize}
  \item Experimental setup.
  \item Present results from human evaluation comparing various systems.
  \item Analyze correlation between evaluation metrics and human judgments.
\end{itemize}

\section{Related Work}
\begin{itemize}
  \item Kevin Knight's work on poetry generation
  \item Any work on writing style (e.g. classification)?  Possibly cite work on author attribution...
  \item work on paraphrase evaluation metrics (David Chen, CCB, etc...)
\end{itemize}

\section{Conclusions}

>>>>

We gathered a set of 20,138 dictionary entries which were scraped from \url{http://www.shakespeareswords.com/}, then used heuristic rules to extract 68,709 phrase/word pairs.  Example
dictionary entries are presented in table \ref{dictionary_example}. As described in \cite{Koehn00}, we estimate phrase translation probabilities based on the frequencies of the translation words/phrases in the target language - the Shakespearean English.

For instance, if we look at the modern English (*probably define EME, Shakespearean, modern/ordinary etc ... I don't know what words to use) word \emph{maybe}, our dictionary lists 4 possible Shakespearean translations. We can obtain the following conditional probabilities for each translation according to the n-gram back off model built on Shakespeare's 36 plays by SRILM toolkit (*ref "SRILM an Extensible Language Modeling Toolkit") \ref{word_frequency}:

So we can estimate that p(PERCHANGE|maybe) = 0.0000790755 / 0.00026264791 = 0.30107035689, and so forth. This method allows us to estimate reasonable translation probabilities in the phrase table. Together with language model consisting of Shakespeare's 36 plays (hold out R&J), we can then choose the most likely translations according to the context.

(*Note that I also changed this table below)

\begin{table}
  \begin{center}
  \begin{tabular}{|l|l||l|l|}
    \hline
    target & source & target & source \\
    \hline
    \hline
    ABATE & shorten & AYE & always \\
    \hline
    CAUTEL & deceit & GLASS & mirror \\
    \hline
    SUP & have supper & VOICE & vote \\
    \hline
  \end{tabular}
  \end{center}
  \caption{Exaple dictionary entries}
  \label{dictionary_example}
\end{table}

(*Note that I also changed this table below)

\begin{table}
  \begin{center}
  \begin{tabular}{|l|l|l|}
    \hline
    conditional probability & target & source \\
    \hline
    \hline
    0.0000790755 & PERCHANCE & maybe \\
    \hline
    0.00003691883 & PERADVENTURE & maybe \\
    \hline
    0.00007524298 & HAPLY & maybe \\
    \hline
    0.00007141065 & HAPPILY & maybe \\
    \hline
    \hline
    total 0.00026264791 & & \\
    \hline
  \end{tabular}
  \end{center}
  \caption{Word frequency in target language}
  \label{word_frequency}
\end{table}

\subsubsection{Out of Domain Monolingual Parallel Data}
As a final baseline we consider a paraphrase system which is trained on out-of-domain data gathered by asking users of Amazon's Mechanical Turk Service 
\cite{Snow08} to describe videos \cite{chen11}.  We combine a phrase table extracted from this out of doimain parallel text, with an in-domain
language model consisting of Shakespeare's 37 plays (*should be 36?).  Although this monolingual parallel data does not include text in the target writing style,
the in-domain language model does bias the generated sentences towards Shakespeare's writing style.

\subsection{Comparison Using Existing Automatic Evaluation Metrics}
Figure \ref{bleupinc} compares a variety of sytstems targeting Shakesperean English using previously the previosly proposed BLEU \cite{Papineni02} and PINC \cite{chen11} automatic evaluation metrics.  A summary of each system is presented in table \ref{systems}.  Notice that the enotes data is quite similar to the original translations,
obtaining a BLEU score of 52.3 when compared against the original text.  Our goal is to produce paraphrases which make many changes to the input, therefore
in the remainder of this paper, we focus on the Sparknotes data for evaluation.

@@

\begin{table}[ht]
  \begin{center}
    \begin{tabular}{|l|p{3in}|}
      \hline
      System & Description \\
      \hline
      \hline
      16and7plays\_36LM & Phrase table learned from all 16 Sparknotes plays (other than R\&J) and language model built from all 36 of Shakespeare's plays, excluding R\&J.
      Uses default Moses parameters. \\
      \hline
      16and7plays\_36LM\_MERT & Same as 16and7plays\_36LM except parameters are tuned using Minimum Error Rate Training \cite{MERT} instead of using the default Moses parameters.\\
      \hline
      16and7plays\_16LM & Phrase table is built from both Sparknotes and Enotes data, and Language model is built from the 16 with modern translations\\
      \hline
      16and7plays\_16LM\_MERT & Same as 16and7plays\_16LM except parameters are tuned using MERT. \\
      \hline
      16plays\_36LM & Only Sparknotes modern translations are used.  All 36 plays are used to train Shakesperean language model. a\\
      \hline
      16plays\_36LM\_MERT & Same as 16plays\_36LM except parameters are tuned using MERT. \\
      \hline
      modern (no change) & No changes are made to the input, modern translations are left unchanged. \\
      \hline
      Dictionary & Dictionary baseline described in section \ref{dictionary_baseline}\\
      \hline
    \end{tabular}
  \end{center}
  \caption{Descriptions of various systems for Shakesperean Paraphrase.  Romeo and Juliet is held out for testing.}
  \label{systems}
\end{table}

\begin{figure}
  \begin{center}
    \begin{tabular}{cc}
      \includegraphics[width=2.4in]{figures/bleupinc1.pdf} & \includegraphics[width=2.4in]{figures/bleupinc2.pdf} \\
    \end{tabular}
  \end{center}
  \caption{Various Shakesperean Paraphrase systems compared using BLEU and PINC.  A brief description of each system is presented in table \ref{systems}.}
  \label{bleupinc}
\end{figure}

\begin{table}[ht]
  \begin{center}
    \begin{tabular}{|l|l|p{1.4in}|p{1.4in}|}
      \hline
      Source & Speaker & Input & Output \\
      \hline
      \hline
      Romeo \& Juliet & Benvolio & he killed your relative , brave mercutio , and then young romeo killed him . & he slew thy kinsman , brave mercutio , and then young romeo kill him . \\
      \hline
      Romeo \& Juliet & Romeo & i can read my own fortune in my misery . & i can read mine own fortune in my woes . \\
      \hline
      Star Wars & Palpatine & If you will not be turned, you will be destroyed! & if you will not be turn 'd , you will be undone ! \\
      \hline
      Star Wars & Luke & Father, please! Help me! & father , i pray you , help me ! \\    
      \hline
      The Matrix & Agent Smith & Good bye, Mr. Anderson. & fare you well , good master anderson . \\
      \hline
      The Matrix & Morpheus & I'm trying to free your mind, Neo. But I can only show you the door. You're the one that has to walk through it. & i 'll to free your mind , neo. but i can but show you the door. you 're the one that hath to tread it . \\
      \hline
      Raiders of the Lost Ark & Belloq & Good afternoon, Dr. Jones. & well met , dr. jones . \\
      \hline
      Raiders of the Lost Ark & Jones & I ought to kill you right now. & i should kill thee straight . \\
      \hline
    \end{tabular}
  \end{center}
  \caption{Example Shakesperean paraphrases generated by the best overall system.}
  \label{examples}
\end{table}

@@

\section{Human Evaluation}
\label{human_evaluation}
Figure \ref{bleupinc} provides some insight into the performance of the various systems, however it is innitially unclear how well the BLEU and PINC
automatic evaluation metrics perform when applied to evaluating paraphrases targeting a specific style of writing.  BLEU and PINC have previously
been shown to have high correlation with human judgements of semantic adequacy and lexical dissimilarity of paraphrase candidates, however no
previous work has evaluated automatically generated paraphrases which target a specific style of writing \cite{chen11}.

@@

For this purpose, we randomly sampled 100 lines from Romeo and Juliet, then two of the authors annotated each sentence and it's Shakesperean
translation with semantic adequacy, lexical dissimilarity, stylistic similarity, and overal quality.
The aggregate results of the human evaluation are displayed in figure \ref{human_judgements}.  Agreement between annotators
measured using Pearson's $\rho$ is displayed in table \ref{annotator_agreement}.

Based on the human evaluation, it appears that the baseline combining paraphrases collected from mechanical turk \cite{chen11} with
a Shakesperean language model has the highest semantic adequacy, however it is also fairly conservative making few changes to the input.
The dictionary baseline, and system trained on parallel modern translations make a roughly comparable number of changes to the input
sentences, but the system trained on modern translations achieves higher semantic adequacy, while being rated higher on style and overall.

These results seem roughly in line with the automatic evalution metrics presented in figure \ref{bleupinc}, however with several important
differences.  Although the video baseline achieves the highest semantic adequacy in the human evaluation, it's BLEU score
is significantly lower than 16plays\_36LM on the Sparknotes data.\footnote{
Note that the BLEU score of 16plays\_36LM is significantly lower when evaluated on the Enotes data.  This makes sense, because the 
16 plays come from Sparknotes. This system is not trained on the 7 Enotes plays which, whose modern translations tend
to be slightly different in style.}
It would appear that in this case BLEU is conflating semantic adequecy with writing style.  Although the paraphrases produced 
by the video baseline have high semantic adequacy, their style tends to differ from the reference translations resulting
in fewer ngram matches, and thus a lower BLEU score.

\begin{table}[ht]
  \begin{center}
    \begin{tabular}{|l|l|l|l|}
      \hline
      Semantic Adequacy & Lexical Dissimilarity & Style & Overall \\
      \hline
      \hline
      0.73 & 0.82 & 0.64 & 0.62 \\
      \hline
    \end{tabular}
  \end{center}
  \caption{Agreement between annotators measured using Pearson's $\rho$.}
  \label{annotator_agreement}
\end{table}

\begin{figure}
  \begin{center}
    \includegraphics[width=5in]{figures/human_judgements.pdf}
  \end{center}
  \caption{Average human judgements evaluating semantic adequacy, lexical dissimilarity, stylistic similarity, and overall quality
    of Shakesperean paraphrase systems} 
  \label{human_judgements}
\end{figure}

\section{Automatic Metrics Evaluating Writing Style}
While PINC and BLEU do seem useful for automatically evaluating paraphrases targeting a  writing style, BLEU tends to conflate the notions of
semantic adequacy with writing style.  When comparing various systems using automatic metrics, however, it would seem useful
to seperate these two critera.  It would seem desirable for our automatic evaluation metrics to be able to distinguish
between a system which generates perfect paraphrases which don't match the target style of writing and a system which
generates sentences in the correct style, but which convey different meaning.

To help address this issue we propse two new automatic evaluation metrics whose goal is to measure the degree to which
autoamtic paraphrases match the target style.  Both metrics assume existence of large corpora in both the source and
target style, but do not require access to any parallel text, or human judgements.

We present a preliminary evalutation of these metrics by measuring their correlation with human judgements, however
we emphasize that here we are only evaluating these metrics with respect to one specific writing style.  We
are cautionsly optimistic that these results will generalize across writing styles, however, as they are based entirely
on ngram statistics.

\subsection{Cosine Similarity Style Metric}
As a first approach automatic evaluation of writing style, we propose a vector-space model of similarity between the system
output and a large corpus of text in both the source and target style.  The intuition is that if there is a large ngram
overlap between the system's output and a large corpus of text in the target style, then the output is more likely to be
stylistically appropriate.

More concretely, we extract ngrams from both the source and target corpus which are then represented as binary
vectors $\vec{s}$, and $\vec{t}$; similarly the output sentence is represented using a vector of
ngrams $\vec{o}$.  
The proposed metric is the normalized cosine similarity between the source and target corpora:
\[
S_{\text{Cosine}}(\vec{o}) = \frac{\frac{\vec{o} \cdot \vec{t}}{\|\vec{o}\| \times \|\vec{t}\|}}{\frac{\vec{o} \cdot \vec{t}}{\|\vec{o}\| \times \|\vec{t}\|} + \frac{\vec{o} \cdot \vec{s}}{\|\vec{o}\| \times \|\vec{s}\|}}
\]

\subsection{Logistic Regression Style Metric}
We also consider a Logistic Regression based approach as an alternative to evaluating writing style.  The idea here, is to estimate the probability that each
sentence belongs to the target style, by using a large source and target training corpus to learn the parameters of a logistic regression model.
This probability is estimated as follows:
\[
%P(\text{style} = \text{target}|\text{output}) \propto \text{exp} \left( \vec{\theta} \cdot \vec{f(\text{output})} \right)
P(\text{style} = \text{target}|\text{sentence}) = \frac{1}{1 + e^{-\left( \vec{\theta} \cdot \vec{f(\text{sentence})} \right)}}
\]
Where $\vec{f(\text{sentence})}$ is a vector of ngrams, and $\vec{\theta}$ is a vector of weights.  
The parameters, $\vec{\theta}$, are optimized on the source and target corpus, where the assumption is that the target corpus
is in the target style, whereas the source corpus is not.\footnote{
  Parameters were optimized using MEGAM \url{http://www.cs.utah.edu/~hal/megam/}.
}

\subsection{Evaluation}
We trained both Logistic Regression and Cosine Similarity evaluation metrics using the original Shakespeare plays and modern translations as
the source and target corpus respectively (holding out Romeo and Juliet), then measured Pearson's Correlation Coefficent between the automatic
evaluation metrics and human judgements reported in section \ref{human_evaluation}.  These results are reported in table \ref{correlation}.

\begin{table}
  \begin{center}
  \begin{tabular}{|l|l|r|}
    \hline
    & & Pearson's $\rho$ \\
    \hline
    \hline
    semantic adequacy & BLEU & 0.35 \\
    \hline
    dissimilarity & PINC & 0.78 \\
    \hline
    style & BLEU & 0.07 \\
    \hline
    style & PINC & 0.20 \\
    \hline
    style & Cosine & 0.37 \\
    \hline
    style & Maximum Entropy & 0.47 \\
    \hline
  \end{tabular}
  \end{center}
  \caption{Correlation between various human judgements and automatic evaluation metrics}
  \label{correlation}
\end{table}

As can be seen in table \ref{correlation}, the correlation between semantic adequacy and BLEU appears smaller than that reported in previous work \cite{chen11}.  Presumably this is
due to the conflation of stylistic differences and semantic adequacy discussed discussed in section \ref{human_evaluation}, however the correlation between BLEU and human style
judgements seems too low to be of practical use.  PINC has very high correlation with judgments on dissimilarity, however we note that it is also highly correlated with human style
judgements.  To understand why PINC is highly correlated with human style judgements, notice that because the systems we are evaluating are targeting Shakesperean English, when changes
are made to the input they are likely to be in the target style.  Although PINC has high correlation with human judgements, it is likely not a useful measure of style in practice,
because for example a paraphrase system which makes many changes to the input, but targets a completely different style will also get a high PINC score.  
Both the Cosine and Maximum Entropy style metrics achieve the highest overall correlation with human writing style judgements, with the Maximum Entropy score performing significantly better.

Finally we note that overall the average automatc metrics seem to agree with agree with human judgements as displayed in figure \ref{style_metrics}.

\begin{figure}
  \begin{center}
    \includegraphics[width=5in]{figures/style_metrics.pdf}
    \end{center}
    \caption{Overall results from comparing automatic style metrics.  Note that the automatic metrics agree with results from human judgements in figure \ref{human_judgements}.}
    \label{style_metrics}
\end{figure}

\section{Related Work}
Although no previous work has investigated paraphrasing modern text into Shakesperean English, or the more general task of paraphrasing while targeting a specific writing
style, there are several strands of related work.

Perhaps most relevant is recent work generating and translating rhythmic poetry \cite{Greene10}.  This work focused on generating text in an appropriate
meter (e.g. iambic pentameter) using finate-state transducers.  In contrast our work does not address the issue of meter, however it should be possible to combine our translation
models with their weighted FSTs to produce Shakesperean paraphrase models which produce output in an appropriate meter.

Much previous work has addressed the task of automatically generating paraphrases \cite{Barzilay03,dolan04,Shinyama03,Das09,bannard05,Callison-Burch08,Kok10}.  In addition several authors have previously proposed 
automatic paraphrase evaluation metrics \cite{chen11,Callison-Burch08b,Bangalore00,liu10}.
We are not aware, however, of any previous work that has addressed the task of generating or evaluating
paraphrases targeting a specific style of writing.

Finally we highlight related work on authorship classification which can be seen as detecting a specific style of writing \cite{Gamon04,Raghavan10}.
This work has not specifically addressed the task of automatically generating or evaluating paraphrases in a specific style, however.

\section{Conclusions}
We have presented initial investigation into the task of automatic paraphrasing while targeting a specific style of writing.  We proposed Shakespere's plays and their
modern translations as a tesbed for this task, and developed a series of paraphrase systems targeting Shakesperean English.  We showed that while existing evaluation
metrics are useful for evaluating paraphrases in this context, BLEU tends to conflate semantic equivelance with writing style giving an incomplete picture of which systems
perform better according to each of these critera.

To address the problems we have demonstrated with previous evaluation metrics applied to this task, we have introduced two new metrics for evaluating writing style.
We measured correlation between automatic metrics and human judgements in the context of paraphrasing writing style, and showed
that our new metrics have better correlation with human judgements than existing metrics in the context of our data.
While this evaluation is limited to one specific style of writing, we are optimistic that these or similar metrics will also perform well when
evaluating other writing styles.

Future work could include automatically translating the remaining 20 of Shakespeare's plays into modern English, which could be benefical to students
of Shakespere's plays and also to future human translators.
